Impact of Pandemic Policies on Rural Indian Women's Mental Health and Economic Stability

### 2024-04-19 outputs/paper.qmd
labels

# Use the updated map in the summarize_models function
summarize_models <- function(models) {
  bind_rows(
    lapply(names(models), function(model_name) {
      model_data <- tidy(models[[model_name]])
      model_data$model <- rename_vars[model_name] %>% coalesce(model_name)  # Rename the model name
      model_data$term <- rename_vars[model_data$term] %>% coalesce(model_data$term)  # Rename the terms
      return(model_data)
    }),
    .id = "model_id"
  ) %>%
    filter(term != "(Intercept)")
}

>>>>

# Use the updated map in the summarize_models function
summarize_models <- function(models) {
  bind_rows(
    lapply(names(models), function(model_name) {
      model_data <- tidy(models[[model_name]])
      model_data$model <- rename_vars[model_name] %>% coalesce(model_name)  
      model_data$term <- rename_vars[model_data$term] %>% coalesce(model_data$term)  
      return(model_data)
    }),
    .id = "model_id"
  ) %>%
    filter(term != "(Intercept)")
}
